%%!TEX root = rapport_netw_model.tex

\section{Brief instructions for an implementation}

\begin{enumerate}
\item Fill and save the Dsu\_1 file (in folder cc). If more than one sims are desired, fill and save the corresponding number of Dsu\_x files, x$=1,2,3,$ etc.
\item Indicate the name of the Dsu\_x files defined in file f\_d.py (in folder cc) and save the file.
\item Fill and save  file ``fi\_node\_id\_ctrl\_type\_category.txt" located in folder ``Control\_Param\_Files''  (in folder cc).
If the last column of this fie values $1$ (it implies that turn ratios will be estimated during the implementation) the fill and save files ``fi\_id\_node\_estim\_turn\_ratio\_param\_dur\_turn\_ratios.txt" and ``fi\_estim\_mrp.txt" and add them in  folder ``Control\_Param\_Files''.
\item Fill  and save the corresponding to the control algorithm, parameter file and add it also in folder ``Control\_Param\_Files'' (in folder cc).
\item 
In a terminal  move to the cc file (by employing the cd command, 
e.g.  cd /Users/jennie/Desktop/sim\_x/sim\_y/cc
\item Write python3.x Simulation.py or time python3.x Simulation.py, with x=is the corresponding version of python3 you have.
e.g. if you have python3.3 you do python3.3 Simulation.py, if you have python3.4 you write python3.4 Simulation.py.
The simulation code runs only under a version of python3.
\end{enumerate}

\section{Brief instructions for a stat analysis}
For doing a statistical analysis included in this code :
\begin{enumerate}

\item copy the produced folder Series\_  by the simulation in file ``Cl\_Stat\_Analysis\_new.py'', in variable  ``val\_name\_fol\_FRes='' (located at the end of this file, line 2465) and save the file.

\item In a terminal, again placed in the cc folder (with the cd command, as when running a simulation) write

time python3.x Cl\_Stat\_Analysis\_new.py or just python3.x Cl\_Stat\_Analysis\_new.py
\end{enumerate}